

% This document is built around the LaTeX APA7 documentclass.  This sets a series of
%  default values, enables sets of options and commands, gives access to typographic
%  features and functions, and assists with citation mechanisms, index generation, and
%  ensuring that we (the authors) don't forget all the necessary bits for our core
%  APA7 documents.


% One of the first things to note is that we cannot use functionality defined in packages
%  until those packages are declared via \usagepackage[<PACKAGE OPTIONS>]{<PACKAGENAME>}
%  so the first thing we do is import values from the options file and then the central file
%  where all packages are defined.  However, this requires \documentclass to be defined.
%  This is also why

%
% The options.tex file is the important file in the project, excluding all of the other
%  most important files.
%
%

% Load our primary options file (options.tex), which sets up our initial set of commands and variables.
%  You will see that we are not using \subimport{} for this as we do later.  This is
% due to the fact that the \subimport call only becomes available when packages are loaded.
%
%
%
%
\input{options}

% Confiure the document with the style options
%  noted above.  Place them here for when we are changing
%  the document they are easier to swap in and out and
%  at the top of the document.
\documentclass[\documentclassoptions]{apa7}

% Load a file named packages.tex which contains a list of
%  packages that add functionality and new tools to our
%  base LaTeX setup - this is the stuff that makes LaTeX go
%  from "Eh" to "Ah! Sweet mystery of life, At last I've found thee"
\input{packages}

\begin{comment}
Import options files (in order) any previously declared option/command
 is replaced with a matching one from lower in this subimport list.
 This gives us, like many other designs patterns here to keep our global
 structure clean by siloing but also to maximize our over-engineering.
\end{comment}

% import options (variables and new commands) at source level.
\subimport{\sourceid}{options}
% import options (variables and new commands) at subject level.
\subimport{\sourceid/\subjectid}{options}
% import options (variables and new commands) at project level.
\subimport{\sourceid/\subjectid/\projectid}{options}

\begin{comment}
Document modes (stu, man, jou, doc) have different sets of required features/calls/variables/settings.
 For example student works require the \course{} value but
 journal articles do not and the document compilation may throw an error if that field is present/absent
 Using a subimport based on the document mode allows us to read in fields and set values specific
 to what that type of document needs but others may not.
 This is identical to the above but a bit of clarity to show why this subimport
 is important beyond its role in over-engineering a simple document environment.
\end{comment}


\subimport{\sourceid/\subjectid/\projectid/\documentmode}{options}

\begin{comment}
BibTeX bibliography/citation files.  These hold references that are called via
 various \cite-style commands (see the APA7 package documentation for APA7 types).
 80of the time I'd just shove them into the top level .bib file and the rest of the
 time I'd put them into a lower .bib file but only because I'd opened the wrong file.
\end{comment}

\addbibresource{default.bib}
\addbibresource{\sourceid/default.bib}
\addbibresource{\sourceid/\subjectid/default.bib}
\addbibresource{\sourceid/\subjectid/\projectid/default.bib}

\begin{comment}
makeindex creates the .idx files for an index (often found at the back of books)
 The index is not generated until a \printindex is called at the location where
 the final index should be inserted in the document.
Note: an external program (makeindex on Linux-based systems) has to be run in
 order to generatet the actual index from the document's code.

If indexgen is set to true (default is set in various options.tex) then build the index.
\end{comment}

\ifthenelse{\equal{\indexgen}{true}}{\makeindex}

\begin{comment}
This is where the actual document + document content begins, I think.
 There is some wuju about what can/must go before or after this point
 and if a document build errors out for this, just swap it above or below.
\end{comment}

\begin{document}

\begin{comment}
subimport is a useful command to allow for documents
 including files by relative instad of absolute paths (e.g., /here/is/our/document.tex vs our/document.tex)

In this case we are using the \sourceid variable set above as part of our path relative path
 which allows us to quickly switch our paths to different document 'trees' while in the same environment.

The source (sourceid) is the largest shell surrounding units of our environment.  The sourceid
 can be on the scale of a company, college program, or a secret society.
\end{comment}

\subimport{\sourceid}{default}

\begin{comment}
If indexgen is set (default is in options.tex) then print the index
\end{comment}


\ifthenelse{\equal{\indexgen}{true}}{\printindex}

\begin{comment}
If listoffiguresgen is set (default is in options.tex) then add the list of figures option
\end{comment}

\ifthenelse{\equal{\listfiggen}{true}}{\listoffigures}

\begin{comment}
Be able to turn off creation of bibliographies - perhaps save paper during proof printing.
\end{comment}

\ifthenelse{\equal{\bibliogen}{true}}{\printbibliography}

\end{document}
